Hello OpenScPCA

### 2024-03-15 analyses/hello-R/notebooks/hello.Rmd
Add outputs and wrapper script

# set results dir (using the analysis project file to find root)
results_dir <- here::here("results")
```

@@

Finally, we will plot the results, faceted and colored by project ID.

@@

>>>>

# set results and plots directories (using the analysis project file to find root)
results_dir <- here::here("results")
plots_dir <- here::here("plots")
```

We will be creating two output files: a table and a plot.
Defining their locations here will make it easy for later users to know what to expect.

```{r}
count_file <- file.path(results_dir, "cell_counts.csv")
plot_file <- file.path(plots_dir, "cell_counts.pdf")
```

@@

And save it to our results directory.

```{r}
readr::write_csv(cell_counts, count_file)
```

Finally, we will plot the results as a histogram, faceted and colored by project ID.

@@

Now let's save the plot.
```{r}
ggsave(plot_file, width = 8, height = 6)
```
